---
title: "Introduction to American Politics"
format:
    html: default
    pdf: 
      documentclass: article
      fontsize: 12pt
      colorlinks: true
      citecolor: DarkViolet
      linkcolor: DarkViolet
      urlcolor: DarkViolet
      geometry: margin=1in
      output-file: "POL102_syllabus"
---


```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tibble)
library(pander)
```

::: {.content-visible when-format="pdf"}

\begin{center}

\vspace{-5em}

\url{ {{< var course.url >}} } \vspace{-1ex}

{{< var course.time >}} {{< var course.days >}} \vspace{-1ex}

{{< var course.location >}} \vspace{-1ex}

{{< var course.semester >}}

\end{center}


## Instructor

{{< var instructor.name >}} \vspace{-1ex}

Email: [{{< var instructor.email >}}](mailto:{{< var instructor.email >}}) \vspace{-1ex}

Office: {{< var instructor.office >}} \vspace{-1ex}

Office hours: Tuesdays 1:30-3:30 pm

:::


::: {.content-visible when-format="html"}

::: {.grid .course-details .course-details-smaller}

::: {.g-col-6}
### Course details

- {{< fa calendar >}} &nbsp; {{< var course.days >}}
- {{< fa calendar-alt >}} &nbsp; {{< var course.dates >}}
- {{< fa clock >}} &nbsp; {{< var course.time >}}
- {{< fa location-dot >}} &nbsp; {{< var course.location >}}
:::

::: {.g-col-6}
### Instructor

- {{< fa user >}} &nbsp; [{{< var instructor.name >}}]({{< var instructor.url >}})
- {{< fa university >}} &nbsp; {{< var instructor.office >}}
- {{< fa envelope >}} &nbsp; [{{< var instructor.email >}}](mailto:{{< var instructor.email >}})
- {{< fa university >}} &nbsp; Office hours: Tuesdays 1:30-3:30 pm
:::

:::

# Syllabus

You can find a PDF version of the syllabus with the weekly schedule on the sidebar of this page.

:::


## Course Overview

This course will provide an overview of the major topics in the study of American politics. The course is arranged in three parts. In the first part of the course, we will talk about the foundations of the American system (the Constitution, federalism, civil rights and liberties). In Part II, we will cover the major institutions of American government (Congress, the presidency, the bureaucracy, and the judiciary). In Part III, we will examine the role of public opinion, political parties, elections, and the media in American politics. In addition to these topics, the course will also introduce you to the methods political scientists use.


## Learning Outcomes

- Develop an understanding of the foundations, major institutions, and principal actors in American politics
- Think critically about the ways in which Americans interact with their political institutions
- Apply the theories and concepts from American politics to current events


## Work and Assessment

### Required Text:

- Levitsky, Steven, and Daniel Ziblatt. 2023. *Tyranny of the Minority: Why American Democracy Reached the Breacking Point.* New York: Crown.
- Kernell, Samuel, Gary C. Jacobson, Thad Kousser, and Lynn Vavreck. 2023. *The Logic of American Politics, 11th Edition.* Thousand Oaks, California: CQ Press/SAGE.



### Course Expectations

Students are expected to attend class and participate during class discussions. This course has both a lecture and a discussion component. The lectures will incorporate the readings assigned for that day/week. I expected you will have completed all readings prior to class and will come prepared with comments and questions. Unless noted otherwise, all readings will be made available on Canvas.

- If you do not have a subscription to *The New York Times*, please sign up through the school here: <https://accessnyt.com/>


### Course Workload

This is a 4-credit hour course, meaning that you are expected to spend 12 hours of work each week (including the 3 hours spent in the classroom). This roughly means that you will spend about 2 hours on readings for each class period, and 3 hours each week working on the different assignments (pace yourself!).


### Assignments and grades

Final course grades will be assigned as follows:

```{r grades, include=FALSE}
grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```

<div class="centered-table">

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc",
               col.names = c("Grade", "Range", "Grade", "Range"))
```

<div>


Final grades will be calculated based on the following components:

**Participation (10%)**: All students are expected to be active participants in class discussions. Our learning experience will be enhanced if you come prepared and ready to share your comments, insights, and/or questions from the material covered in the lectures and readings with the rest of the class.

  - <ins>*Attendance policy:*</ins> Attendance is part of your participation grade, and while there is no separate grade for attendance it is a prerequisite for in-class participation. That said, to accommodate unforeseeable circumstances, you have three *unexcused* absences that will not affect your participation grade. Please let the instructor know about any excused absences you anticipate during the semester.


**Three Response Papers (10% each)**: Throughout the course, we will talk about the state of American democracy. After each of the major sections of the course (foundations, institutions, and the public) you will return to the question of whether American democracy is fragile or stable. In these short papers (2 double-space pages) you will discuss how the different foundations, institutions, or players in American politics contribute to the resilience or erosion of democracy in the United States.

**Campaign Memo Assignments**: The major assignment in this course will conclude in a campaign memo for a member of the House of Representatives. You will pick a representative and write a campaign strategy memo. This memo should be directed to campaign staff and should include clear actions and sufficient (but not overwhelming) justification. There are four different assignments that will be due throughout the semester: the demographics of the member's constituency, the roll call record of the member, and the topics the campaign should focus on:

1. Congressmember Profile (10%): This 1-2 page, single-spaced, paper should describe the political career (electoral history, roll-call record, bill sponsorship, etc.) of the member of Congress you chose for your campaign memo.

2. Congressional District Profile (10%): This 1-2 page, single-spaced, paper should describe the demographic and political characteristics of the congressional district your member of Congress represents.

3. Full draft for peer review (5%): Using the research you did in the previous two papers, this is the first full draft of the campaign strategy memo (3-5 single-spaced pages) directed at the campaign staff. You will receive and give feedback from/to a peer.

4. Final draft (15%): This is the final draft of your campaign strategy memo (3-5 single-spaced pages) where you should incorporate the feedback you received on your previous draft.


- Papers must be submitted via Canvas. Late submissions will be penalized with one point off for each 24-hour period after the due date.



**Midterm and Final Exam (20% each)**: There will be a midterm and a final exam that students will complete on Canvas. These exams will assess your familiarity with the terms and theories in the American politics literature that we will have covered in class.



## Course Conduct

Students in this course come from a variety of social, economic, and political backgrounds. As in bound to be the case when we talk about politics, we will discuss many topics that might be controversial or of a sensitive nature for some or all in our group. Our goal in this class is to gain an understanding of how political scientists study American politics and to use these tools to help us have productive discussions of contemporary politics. Derogatory comments toward other students or members of a particular groups will not be tolerated.


## Communication Policy

If you have questions about class in general or about a specific assignment, you can email me or come by my office. You can expect a response within 24 hours (unless you email me on Friday). Students are also more than welcome to attend office hours, as this is time set aside specifically for you. In addition, if my office door is open, feel free to stop by. Please note that I will not be "pre-grading" assignments, but I am happy to answer clarifying questions about them either via email or, preferably, during office hours.


## Regrading Policy

If a student wishes to appeal a grade, they must do so in writing within one week of receiving their graded assignment back. The student must indicate clearly what part of the assignment's grading they disagree with, making sure to respond to the instructor's comments in that section and making their case for why they should not have been deducted points. These requests should be done via email and the subject name should read "POL 102 Regrading request - [Name of assignment]." 


## Honor Code

Students are expected to do their own work and cite sources appropriately. Plagiarism will not be tolerated. In other words, students will be held to the standards of the Agnes Scott Honor System to which they agreed when enrolling at this institution. The Agnes Scott College honor code embodies an ideal of character, conduct, and citizenship, and is an important part of the College’s mission and core identity. This applies especially to academic honesty and integrity. Passing off someone else’s work (or Chat GPT's) as your own represents intellectual fraud and theft and violates the core values of our academic community. To be honorable, you should understand not only what counts as academic dishonesty, but also how to avoid engaging in these practices.


You are responsible for the content of any work submitted for this course. The use of artificial intelligence (AI) to generate a first draft of text is permitted, but you must review and revise any AI-generated text before submission. AI text generators can be useful tools but they are often prone to factual errors, incorrect or fabricated citations, and misinterpretations of abstract concepts. I neither encourage nor discourage their use, but utilize them with caution.



## Course Accessibility and Academic Accommodations

Agnes Scott College views disabilities as an integral part of the rich diversity of our community and strives to make all learning experiences as accessible as possible.  If you are a student who receives academic accommodations through the Office of Accessible Education, please schedule a meeting with me within the first two weeks of classes to discuss how your accommodations will be implemented for this course.  During this meeting, you are not expected to disclose any details concerning your disability, though you may discuss these details at your discretion.

If you are a student with a disability---physical, medical, psychological, or learning-specific---and have not connected with Accessible Education to discuss your accessibility needs, please visit the [main Office of Accessible Education webpage](https://www.agnesscott.edu/academicadvising/accessible-education/index.html) to learn more about accommodations, helpful resources and support, available through the Office of Accessible Education.  Students who register for accommodations during the semester should schedule a meeting with me after accommodations have been approved by the Office of Accessible Education.


## Wellbeing and Mental Health

The wellbeing and mental health of students is important; if you are having trouble completing your coursework, please reach out to the [Wellness Center](https://www.agnesscott.edu/wellnesscenter/index.html). Agnes Scott College provides cost-free mental health services to help you manage personal challenges that threaten your personal or academic well-being. If you believe you are experiencing unusual amounts of stress, sadness, or anxiety, please contact the Wellness Center and ask about their [Counseling and Psychological Services](https://www.agnesscott.edu/wellnesscenter/counseling/index.html).


## Title IX

Agnes Scott is here to help you if you have experienced any form of sexual harassment or violence, dating or domestic violence, or stalking. Please talk to any faculty or staff member with whom you feel comfortable. Faculty and staff members want to support you and have been trained to help. They will also inform the Title IX office so that you learn about options available to you. If you do not want college administrators to know what you have experienced, you may talk to the chaplain, as well as nurses or counselors in the Wellness Center with complete confidentiality. They will not tell anyone what you share with them unless you give your express permission. You may contact the Title IX Coordinator directly at <T9Coordinator@agnesscott.edu>.


## Diversity and Inclusion

Agnes Scott is a diverse and inclusive community. As one of the most diverse colleges in the nation, ASC is ideally positioned to be the model of a diverse and inclusive community that society can aspire to be. Such diversity raises the intellectual quality of the classroom experience, creating a unique environment for learning to understand and navigate the challenges of our times. By studying, living, and playing together, Agnes Scott College’s remarkably diverse student body hones the habits of mind, skills, and knowledge essential to ethical and innovative leadership in our increasingly heterogeneous and global society.  As such, this course adheres to the principles of diversity and inclusion as integral to the Agnes Scott community and respects people from all backgrounds. As a first step, this course affirms people’s decisions about gender expression and identity and will use each other’s preferred names and gender pronouns at all times.



## Center for Writing and Speaking

The Center for Writing and Speaking offers one-on-one appointments with trained peer tutors who can help you improve your written and oral communication skills. You are encouraged to use this resource when working on your class assignments to make your arguments more compelling, your sentences clearer, and persistent grammatical errors nonexistent. You can schedule an appointment at <https://www.agnesscott.edu/center-for-writing-and-speaking/index.html>.


## Syllabus Change Policy

This syllabus is only a guide for the course and is subject to change with advanced notice.


::: {.content-visible when-format="pdf"}
  
## Schedule

{{< include content/01-week1.qmd >}}

{{< include content/02-week2.qmd >}}

{{< include content/03-week3.qmd >}}

{{< include content/04-week4.qmd >}}

{{< include content/05-week5.qmd >}}

{{< include content/06-week6.qmd >}}

{{< include content/07-week7.qmd >}}

{{< include content/08-week8.qmd >}}

{{< include content/09-week9.qmd >}}

{{< include content/10-week10.qmd >}}

{{< include content/11-week11.qmd >}}

{{< include content/12-week12.qmd >}}

{{< include content/13-week13.qmd >}}

{{< include content/14-week14.qmd >}}

{{< include content/15-week15.qmd >}}

{{< include content/16-week16.qmd >}}

{{< include content/17-week17.qmd >}}

{{< include content/18-week18.qmd >}}

:::

{{< include index_title.qmd >}}

